---
title: "BBets Project"
author: "Evangela McGarity"
date: "3/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction  

The question is how much money is won/lost on a bet that at least two people have the same b'day in a class of 35.  Instructor wagers 2:1 

Instuctor has done this 15 times,  
1.How much money does DR  J win/lose with 15 classes and 35 students?
2. how much money should DR J pay out per bet to make this a fair game with 35 students?  
3. how many students would have to be in the class for a 2:1 bet to be fair?   
 
 
```{r}
days = 1:365
nStudents = 35
nBets = nStudents *15


saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:nBets){
    sampleClass = sample(days,nStudents, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == nStudents) bank = bank - 2
    else bank = bank + 1
  }
saveArray[k]= bank
}

```
 
histogram of bank amounts.   

```{r}
hist(saveArray)
```
Answer question #1 

Dr. J makes $235

```{r}
print('average amt:')
print(mean(saveArray))
```

  Answer question #2
  Around $4
  
  Answer question #3
  35 students